\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{G Thomas Hudson}

\personal
    [https://github.com/ghomasHudson]
    {Lune View\newline Wrayton, LA6 2QU}
    {+447450213517}
    {g.t.hudson@durham.ac.uk}

\section{Experience}

\begin{eventlist}

\item{June 2016 -- September 2016}
     {}
     {Cybersecurity Summer School}

Intensive internship program exploring the detail of practical cybersecurity including Penetration Testing, Information Assurance, Industrial Control Systems \& Internet of Things, Secure Coding, Reverse Engineering and Web Security.

\item{June 2015 -- September 2015}
     {\href{http://www.hut8strategicmobile.com}{Hut8 Strategic Mobile}}
     {Software Engineer}

Development and testing of web based software projects for clients in a small team. Lead a project to support solar roof installations (including innovative use of the Google Maps API to calculate roof area). Developed key skills in client communication, scrum agile development and unit testing as well as technical skills in HTML5, CSS3, Bootstrap, jQuery, NodeJS and AngularJS.

\item{September 2014}
     {\href{http://checkpoint-safety.com/}{Checkpoint}}
     {Sales/Marketing Assistant }

Solving a range of business problems through the application of  computers. Involved Database management, programming, working with users to devise user-friendly systems and basic HTML.

% \item{June 2014 -- September 2014}
%      {A. Whitaker}
%      {Assistant Gardener}

% \item{January 2012 -- June 2014}
%      {Queen Elizabeth School}
%      {Cleaner}

\end{eventlist}

\subsection{Other Experience}

Assistant Gardener - June 2014 -- September 2014 \\
Cleaner - January 2012 -- June 2014 \\
Volunteer Assistant Tennis Coach - 2008 --2012
\vfill\null
\columnbreak
\section{Education}

\begin{yearlist}

\item[MEng Computer Science]{2014 -- present}
     {Durham University}
     {Currently working on projects in Natural Language Processing and Machine Learning.
     }

\item{2007-2014}
     {Queen Elizabeth School}
     {A-Levels at Grade A in Computing, Physics and Mathematics}

\end{yearlist}

\section{Public projects}

\begin{yearlist}

\item{2013}
     {graphVisualiser}
     {Teaching tool for graph theory}

\item{2015}
     {\href{http://community.dur.ac.uk/g.t.hudson/durhamTimetableApp/}{Pretty Timetable}}
     {Minimalist skin and iCal converter for the Durham University timetable. Built using Bootstrap}

\item{2016}
     {pyWebcamSteg}
     {Webcam steganography-based annonymising proxy}
\end{yearlist}

\section{Software skills}

\begin{factlist}

\item{Good level}
     {Java, MySQL, Javascript, HTML5, CSS3, Bootstrap, jQuery, Python, C, PHP, HTML, CSS, NodeJS, AngularJS, MongoDB, git}

\item{Intermediate}
     {C++, \LaTeX, Prolog, Haskell}

\item{Basic level}
     {C\#, Lua, CUDA, OpenMP}

\end{factlist}

\end{document}
